---
title: "Tidy Tuesday - Tweets"
author: "Richard G. Gardiner"
date: "1/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data and Packages

```{r, echo = FALSE}
library(tidyverse)
library(tidytext)
```

```{r}
tidy_tuesday <- readRDS("tidytuesday_tweets.rds")
rstats <- readRDS("rstats_tweets.rds")
tidy_tuesday$document <- "tidy_tuesday"
rstats$document <- "rstats"
all_tweets <- rbind(tidy_tuesday, rstats)
```

Let's look at who is the most favorited in tweets.  This first table shows the total number of times someone favorited a tweet, grouped by screen_name.  We see that some common names are appearing, such as Rbloggers (who tweets far more than anyone else in the group) and some of the other big names in the R community (hadleywickham and drob).  Note that I looked at the mean, but the top favorited come from individuals who rarely tweet and had one tweet go viral.
```{r}
top_favorited <- all_tweets %>%
  group_by(screen_name) %>%
  summarise(sum_favorited = sum(favorite_count),
            total_tweets = n()) %>%
  top_n(10, sum_favorited) %>%
  arrange(desc(sum_favorited))
```

# Tweets Over time

```{r}
library(lubridate)
all_tweets$date <- date(all_tweets$created_at)

all_tweets %>%
  group_by(date, document) %>%
  count(date) %>%
  ggplot() +
  geom_line(aes(x = date, y = n, colour = document)) +
  ylab("Number of Tweets")

ggsave("TweetsOverTime.png")
```

# What do the Most Favorited People Talk About?

Now filtering for the people who were the most favorited?  First we need to unnest_tokens using the `tidytext` package.  Then we will only look at those that were the top favorited people.  Lastly, we caclculate the tf-idf and then graph the results!
```{r}
tidy_text <- all_tweets %>%
  filter(is_retweet == "FALSE") %>%
  unnest_tokens(word, text, token = "tweets") 

tidy_text_top_favorited <- tidy_text %>%
  filter(screen_name %in% top_favorited$screen_name) 

tf_idf <- tidy_text_top_favorited %>%
  count(screen_name, word, sort = TRUE) %>%
  bind_tf_idf(word, screen_name, n) %>%
  arrange(desc(tf_idf))

tf_idf
```

I had to take out "dataandme" because of weird text issues.
```{r}
tf_idf %>%
  filter(screen_name != "dataandme") %>%
  group_by(screen_name) %>%
  top_n(12, tf_idf) %>%
  ungroup() %>%
  mutate(word = reorder(word, tf_idf)) %>%
  ggplot(aes(word, tf_idf, fill = screen_name)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ screen_name, scales = "free") +
  ylab("tf-idf") +
  coord_flip()

ggsave("TopTweetersAndSubject.png")
```


